\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
done with video capture mode in the experiments.

\subsection{Privacy extraction mode}

During the experiment of privacy extraction, we chose \textit{HUAWEI P30}, a
smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the
target device.  In the privacy extraction mode, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the valuable
information from video stream.  When the victim viewed text or photos with
text, \tool used the techniques of Optical Character Recognition (OCR) to
extract text from corresponding video frames.  In this experiment, the attacker had
successfully extracted text like name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which the enables
attacker to identify payment code in the video stream and perform transactions
without the password. As this is also a part of our case study, more details about
the data extracted can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.

\fengwei{I don't understand the following sentence. Both modes need to capture
the video stream. Don't understand why it is more power-efficient.}
\hongyi{Reasonable, changed to other advantage}
After the
experiment, we have found that as privacy extraction mode only needs to
process the victim's video stream locally, it does not need to transmit the real-time video back to the attacker. This mode is useful when there is no stable network connection between \tool and the attacker.

>>>>

\subsection{Video Capture Mode}

During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30}, a
smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the
target device.  In the privacy extraction experiment, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the sensitive
information from the video stream.  When the victim viewed text or photos with
text, \tool used the techniques of Optical Character Recognition (OCR) \fengwei{do we need a reference for OCR?} to
extract text from corresponding video frames. In this experiment, the attacker had
successfully extracted text like name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which enables
an attacker to identify payment code in the video stream and perform transactions
without the password. As this is also a part of our case study, more details about
the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.

%\fengwei{I don't understand the following sentence. Both modes need to capture
%the video stream. Don't understand why it is more power-efficient.}
%\hongyi{Reasonable, changed to other advantage}
Note that the video capture mode only needs to
process the victim's video stream locally, it does not need to transmit the real-time video back to the attacker, which is needed when the network connection between \tool and the attacker is not stable. 
%This mode is useful when there is no stable network connection between \tool and the attacker.
